Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-08 ms.tex
starting to describe experiments with reddening residuals

We additionally investigated spatial cuts which did not resolve the 
dominant problems noted in the reddening residuals:

>>>>

We additionally investigated the following spatial cuts which did not resolve 
the dominant problems noted in the reddening residuals:
\begin{itemize}
\item Separating Celestial north and south.
\vspace{-3mm}
\item Separating Galactic north and south.
\vspace{-3mm}
\item Separating inner and outer Galaxy.
\vspace{-3mm}
\item Combining the above two sets of cuts i.e. separating the Galaxy into
quadrants. 
\vspace{-3mm}
\item Combining these spatial cuts with the dust model changes of the previous
list.
\end{itemize}

However, we did find that changing the zero level offsets of the input maps 
had a significant effect on the strength of the anticorrelation between
reddening residual and $T_2$. In particular, we experimented with perturbing 
the zero level offset of \PLANCK~857 GHz while correspondingly changing the 
zero levels of the remaining \PLANCK~maps based on the prescription of 
$\S$\ref{sec:relzero}. We also experimented with changing the zero level of SFD
\verb|i100|, independent of the other zero levels. Unfortunately, completely
flattening the reddening residual dependence on $T_2$ required unreasonably 
large zero level changes. For example, flattening the $T_2$ residual required
adding $\gtrsim$0.6 MJy/sr to the \verb|i100| map. Furthermore, we note that 
even relatively large zero level modifications had virtually no effect in 
eliminating the `bend' versus $E(B-V)_{SFD}$. Thus, simply changing the
zero level offsets showed a bit of promise in rectifying the residual 
temperature dependence, but of itself was not a sufficient solution.

The ony solution we were able to identify that both removed the `bend' vs.
$E(B-V)_{SFD}$ and the temperature dependence of the residual was cutting 
out the ecliptic plane, restricting to $|\beta|>20^{\circ}$ . In this case, we 
completely eliminated the bending behavior of the residual versus 
$E(B-V)_{SFD}$, and significantly reduced the $T_2$ dependence (see Figure
QQ)

% but required offsets too big

% but then we tried ECL cuts, and in combination with modest offsets, that 
% worked
